rotation_runs2020_sam

### 2020-01-08 inst/documents/rotations_runs2020_sam.rmd
edit sams file for 160k runs to output tot_gens and mean mortality

---
title: "rotation_runs2019"
output: pdf_document
#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
---

An rmarkdown document that can be modified and knit to run scenarios within a specified experiment.
Output files are saved to the specified outFolder.

@@

outFolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
```

@@

nscenarios <- 200
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

# to move the pdf of a preceeding run of this file to a saved location
# RUN the line above and below after knitting the file
# ASSUMING id_expt still set to previous run and still same day
# BEWARE that id_expt will not be set correctly in home env if file was knitted
#file.rename("rotation_runs2019.pdf",paste0(outFolder,format(Sys.time(), "%Y-%m-%d-"),id_expt,"-results-figs.pdf"))

# old ways of doing it
# infile_multi <- 'rotations-experiments-creating-201909.xlsx'
# infile_multi <- system.file("extdata", infile_multi, package = "rotations", mustWork = TRUE)
# inex_all <- read_excel(infile_multi)

# older way with individual experiment files
# to add new files currently need to reinstall package because infiles are in extdata
# infile <- "expt-A2-freq-insame-costs-nodisp.csv"
# infile <- "expt-A4-freq-insame-costs-disp.csv"
# # get the id for the expot to include in outfilenames, specifies experiment attributes
# id_expt <- substr(infile,6,7)
# # read an experiment file specifying ranges
# inex <- read_in_expt(infile, nscenarios=nscenarios)

inex <- read_in_expt(nscenarios = nscenarios, multi=TRUE, id_expt=id_expt)

# text to go at start of document
cat("\nThere are 16 potential experiments :\n\n    ")

cat("Experiment :",id_expt," scenario number is pagenum -1 \n\n    ")

cat("Experiment key :\n    ")
cat("A: resistance frequency threshold, insecticides the same\n    ")
cat("B: resistance frequency threshold, different insecticides\n    ")
cat("C: mortality threshold, insecticides the same\n    ")
cat("D: mortality threshold, different insecticides\n    ")

cat("1: no costs, no dispersal\n    ")
cat("2: costs, no dispersal\n    ")
cat("3: no costs, dispersal\n    ")
cat("4: costs, dispersal\n    ")

cat("\nNumbers on the right are the number of generations that this insecticide is in use and the corresponding resistance is below threshold.\n   ")

cat("\nOn each page a Sequence is at the top and an annual Rotation at the bottom.")

# create an object containing inputs for all scenarios
linmulti <- set_run_inputs(inex=inex)

# run all scenarios
for(i in 1:nscenarios)
{
  #message should output to the R markdown console
  if (i%%200 == 1) message("scenario ",i," of ",nscenarios," ",Sys.time())

@@

  #record rotation rot interval locally otherwise it get soverwritten by 0
  rot_rot_interval <- linputs$rot_interval

  #to add label between plots in output doc
  #this adds label underneath, not my intention but does the job
  cat("\n\n\\pagebreak\n    ") #needs results='asis' in the chunk options
  #cat("scenario",i,"\n     ") stopped plots from aligning
  #instead just remember that scenario number is pagenum -1

@@

  #can save partial outputs in case doesn't make to end
  if (i==nscenarios | i%%1000 == 0)
  {

    # save object containing inputs and results as rda for analysis
    # by default saved to inst/documents folder
    save(df_res_all, file=paste0(outFolder,format(Sys.time(), "%Y-%m-%d-%H-%M-"),'df_res_all_rot',id_expt,nscenarios,'.rda')) #paste0(outFolder,'*.rda')) 
    # also save the experiment input file
    save(inex, file=paste0(outFolder,format(Sys.time(), "%Y-%m-%d-%H-%M-"),'inex-',id_expt,'.rda'))   
  }

@@

```

>>>>

---
title: "rotation_runs2020_sam"
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

An rmarkdown document to run 160k runs, 10k from each of 16 experiments.
Sam Jones runs on fast machine overnight.
Output files are saved to the specified outFolder.

rotation_runs2019.Rmd is similar but allows experiments to be run individually and to generate a pdf of results for an experiment per run.

@@

#Sam: Andy, it appears that TinyTex is also required 
library(tinytex)
outFolder <- "I:/Rotations/Results_Jan/"
```

@@

Stime = date ()  
cat("startTime", Stime, "\n")

plotyn <- 0 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

runList<-c('A1','A2','A3','A4','B1','B2','B3','B4','C1','C2','C3','C4','D1','D2','D3','D4')
#runList<-'A1'

nscenarios <- 10

for(r in runList){
  id_expt <- r

# # read an experiment file specifying ranges
# inex <- read_in_expt(infile, nscenarios=nscenarios) 
inex <- read_in_expt(nscenarios = nscenarios, multi=TRUE, id_expt=id_expt)

# create an object containing inputs for all scenarios
linmulti <- set_run_inputs(inex=inex)
# run all scenarios
for(i in 1:nscenarios)
{
  #message should output to the R markdown console
  if (i%%200 == 1) message("scenario ",i," of ",nscenarios," ",Sys.time())

@@

  #record rotation rot interval locally otherwise it gets overwritten by 0
  rot_rot_interval <- linputs$rot_interval

@@

  #can save partial outputs in case doesn't make to end
  #if (i==nscenarios | i%%1000 == 0)
  #{

    # save object containing inputs and results as rda for analysis
    # by default saved to inst/documents folder

  #}

@@

save(df_res_all, file=paste0(outFolder,'df_res_all_rot',id_expt,nscenarios,'.rda')) #paste0(outFolder,'*.rda')) 
    # also save the experiment input file
    save(inex, file=paste0(outFolder,format(Sys.time(), "%Y-%m-%d-%H-%M-"),'inex-',id_expt,'.rda'))

Etime = date ()	
cat("endTime", Etime, "\n")

cat(Stime,Etime)
}
```
